STAT 133 Final Project: Visualizing Berkeley Police Data

### 2016-08-09 final_paper/finalpaper.Rmd
rebecca edit

Moving on from the stop data, we considered the available jail data and arrest data for the city of Berkeley, which is not necessarily dependent on the stop data. Two of the most interesting variables to consider in these two data sets were also race and age. We decided the examine the percent of people arrested and the percent of people jailed in Berkeley by both age and race. Figure 17 is a visualization. Note that the following percentages are related to the number of total people jailed or the number of people arrested, respectively, and we have not adjusted the data relative to the population of Berkeley.

>>>>

Moving on from the stop data, we considered the available jail data and arrest data for the city of Berkeley, which is not necessarily dependent on the stop data. Two of the most interesting variables to consider in these two data sets were also race and age. We decided the examine the percent of people arrested and the percent of people jailed in Berkeley by both age and race. Figure 17 is a visualization. Note that the following percentages are related to the number of total people jailed or the number of people arrested during a recent 30 day time frame, respectively, and we have not adjusted the data relative to the population of Berkeley. It is interesting to note that the proportions of arrests and jailings during this time are nearly identical, since these arrests and jailings occur during the same time frame. The data suggests that being jailed after being arrested in Berkeley is almost certain, and that this is true for all races. However, note that the proportion of Blacks being arrested and jailed is more than the other races, in spite of Berkeley being a city of mostly White people.
